---
title: "API Workshop - "Solutions""
date: "10/20/2020"
output: 
  html_document:
    toc: true
---

Workshop Recording: https://www.youtube.com/watch?v=kZU240u9H3E  

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages(c("httr", "jsonlite"))

library(httr)
library(jsonlite)
library(tidyverse)
```

# Example 1: Basic GET Request
http://open-notify.org/Open-Notify-API/People-In-Space/
```{r}
res = GET("http://api.open-notify.org/astros.json")
```

```{r}
fromJSON(rawToChar(res$content))
```


# Your Turn: Basic GET Request
http://open-notify.org/Open-Notify-API/ISS-Location-Now/
```{r}
res2 = GET("http://api.open-notify.org/iss-now.json")
print(res2)
fromJSON(rawToChar(res2$content))
```

# Example 2: GET Request w/Query
http://api.open-notify.org/iss-pass.json?lat=LAT&lon=LON  
Coordinates of OSU: 40.0067, 83.0305
```{r}
res = GET("http://api.open-notify.org/iss-pass.json?lat=40.0067&lon=83.0305")
json_res = fromJSON(rawToChar(res$content))
```

```{r}
time_df = json_res$response

time_df = mutate(time_df, risetime_formatted = lubridate::as_datetime(risetime))
```

Here's also another way to add query parameters, it's generally recommended since it's easier to format, and you can pass variables to it:
```{r}
res = GET("http://api.open-notify.org/iss-pass.json", query = list(lat = 40.0067, lon = 83.0305))
print(res)
json = fromJSON(rawToChar(res$content))
```

# Your Turn: GET Request w/Query (Sunset-Sunrise API)
https://sunrise-sunset.org/api
```{r}
res = GET("https://api.sunrise-sunset.org/json", query = list(lat = 40.0067, lng = 83.0305, date = "today"))
print(res)
json = fromJSON(rawToChar(res$content))
print(json)
```

# Example 3: GET Request w/API key Authentication (Spotify API)
https://developer.spotify.com/documentation/web-api/quick-start/
https://developer.spotify.com/console/get-search-item/

Remember to update this oauth token to your own since this one will be expired.

```{r}
spotify_oauth_header = "Bearer BQBp21_zCAcp2Xes-7lZi-CwyYFP0NfEz_7uUqMUWaygh2boyoB5UUfWe0JNYUxwDWR-BV5UCiixqm914eDtLJDOW60neNXtrwsX9WWkBlUVNJcvct_Gla4CnrC8g3kaKqBG3opx7o3KfswnE8JgUQ8"

res = GET("https://api.spotify.com/v1/search?q=Muse&type=artist", config = add_headers(c(authorization = spotify_oauth_header)))

json_res = fromJSON(rawToChar(res$content))
```


# Your Turn: GET Request w/API key Authentication (Spotify API)
https://developer.spotify.com/console/get-audio-analysis-track/

```{r}
GET("https://api.spotify.com/v1/tracks/7mtYsNBYTDPa8Mscf166hg", config = add_headers(c(authorization = spotify_oauth_header)))
```


```{r}
res = GET("https://api.spotify.com/v1/audio-analysis/7mtYsNBYTDPa8Mscf166hg", config = add_headers(c(authorization = spotify_oauth_header)))

track_analysis = fromJSON(rawToChar(res$content))
```

```{r}
track_analysis
```